## Transform

### Challenge 4
Create a new variable `clean_taxis` by piping the taxi data through the `filter` function.

You'll need to decide what range of data points to use.
```{r}
clean_taxis <- taxis %>% filter(trip_distance < 100, passenger_count > 0, passenger_count < 10, total_amount > 0, total_amount < 1000, RateCodeID ==1)
```

Re-make the raster plot and see if it looks more reasonable.
```{r}
clean_taxis %>% dbplot_raster(x=trip_distance, y=total_amount)
```

### Challenge 5
To answer our brief we need to look at the locations where most pickups and dropoff are happening.

Ultimately we want to end up with a table of data that looks something like this:

| LocationID | pickups | dropoffs | total |
| ---------- | ------- | -------- | ----- |
|     1      |  1234   |   5678   |  6912 |

Let's start with pickups.

We need to
- select only the pickups column (PULocationID) and give it a new name `LocationID`
- group_by the newly named column to collect all the same locations together
- sum up the taxi rides in each group using `summarise` and the count function `n()`
- sort the final result by `LocationID` using `arrange()`

```{r}
pickups <-  clean_taxis %>% select(LocationID = PULocationID) %>% group_by(LocationID) %>% summarise(pickups = n()) %>% arrange(LocationID)

pickups
```


Now do the same for drop-offs
```{r}
dropoffs <-  where_taxis %>% select(LocationID = DOLocationID) %>% group_by(LocationID) %>% summarise(dropoffs = n()) %>% arrange(LocationID)

dropoffs
```

### Challenge 6
Join the pickups and dropoffs tables together `by` their shared `LocationID` column and sort the result.
```{r}
pickdrops_spark <- left_join(pickups, dropoffs, by="LocationID") %>%  arrange(LocationID)
```

```{r}
pickdrops_spark
```

### Challenge 7
Since the the number of locations is not that big, we can now bring the data back into R using `collect()`
```{r}
pickdrops <- pickdrops_spark %>% collect()
```

### Challenge 8
To complete the final bit of data transformation, add a total column using `mutate` %>% mutate(Total = dropoffs + picksups)

```{r}
pickdrops %>% mutate(total = dropoffs + picksups)
```
