## Visualise

```{r}
library(tmaptools)
library(sf)
library(ggplot2)
```

### Challenge 9
Read in the map shape file from https://www1.nyc.gov/site/tlc/about/tlc-trip-record-data.page
```{r}
map <- st_read(___)
```

What does the map look like?
```{r}

```

### Challenge 10
We need to append the map with our pickup and dropoff data
```{r}
map <- append_data(___, ___)
```

Plot the map again and you'll see our new data appears, but it's not very nice to look at.
```{r}

```

### Challenge 11
To make our maps nicer to look at we'll use ggplot. Plot 3 maps, one for pickups, dropoffs and total.
```{r}
ggplot(___)+geom_sf(___)+ scale_fill_gradient(low= "dark grey", high="yellow")
ggplot(___)+geom_sf(___)+ scale_fill_gradient(low= "dark grey", high="yellow")
ggplot(___)+geom_sf(___)+ scale_fill_gradient(low= "dark grey", high="yellow")

```


### Challenge 11
To make our recommendations to the taxi company, let's do a simple plot of the top 10 pickup locations
```{r}
top_pickups<- ___ %>% select(___, zone, borough) %>%  arrange(desc(___)) %>%  ___(10)
```

```{r}
___(___, aes(x= ___, y = reorder(zone, pickups)))+ ___(size=3)
```

**IMPORTANT** Disconnect spark when finished to avoid running out of processing memory (RAM)
```{r}
spark_disconnect(sc)
```
