
# Becoming a piping pro

To using the pipe operator %>% (shortcut cmd+shift+m) we need to use a library called magrittr
```{r}
library(magrittr)
```

First load the favourite numbers data that you've downloaded from github
```{r}
favouriteNumbers <- 
```

## Challenge 1
Pipe the favouriteNumbers data into summary() to get an impression of what the data is like. What do you notice about peoples' favourite numbers?
```{r}
favouriteNumbers %>% 
```

## Challenge 2
The summary above shows us that the numbers are not simple, e.g. between 1 and 100 - we have some strange gigantic numbers! For your next challenge, you are going to use piping to find the number of **unique** numbers that people chose. 

```{r}
favouriteNumbers 
```

## Challenge 3
We saw that there are a lot more numbers than we probably expected. Let's narrow this down by using piping to create a **subset** of the data between 0 and 20 and saving it to a new variable called smallerNumbers.

```{r}
smallerNumbers <- favouriteNumbers
```

## Challenge 4
Now you've got a subset of the data you can plot a histogram to see which is the most popular number. Hint, you'll need to pipe a specififc column of the smallerNumbers dataframe.

```{r}
smallerNumbers$
```

## Challenge Extremo
The favouriteNumbers data corresponds to around 30,000 records. You can condense this information by creating a frequency table. Your challenge is to use piping to create a frequency table and export it as a CSV file. Hint, You'll need to take the resulting table and recast it as a data frame before you export.

```{r}
favouriteNumbers$numbers 
```

You can find the csv file in the Files panel and you can view it by clicking on it.